---
title: "Interact with local models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interact with local models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Intro

[LlamaGPT-Chat](https://github.com/kuvaus/LlamaGPTJ-chat) is a command line chat 
application. It integrates with the LLM via C++. This means that it will only
work with LLM's that have been in the same language.  There are few available
today that are free to download and use. Because they are in C++, the models are 
able to run locally on your computer, even if there is no GPU available.  Most 
of the models are quite fast in their responses. By integrating with LlamaGPT-Chat, 
 able to access multiple types of LLM's with only one additional back-end
within `chattr`.

## Installation

To get LlamaGPT-Chat working you machine you will need two things:

1. A version of LlamaGPT-Chat that works in your computer

1. An LLM file that works with with the chat program

### Install LLamaGPT-Chat

LlamaGPT-Chat will need a "compiled binary" that is specific to your Operating
System.  For example, for Windows, a compiled binary should be an *.exe* file. 


The GitHub repository offers pre-compiled binaries that you can download and use: [Releases](https://github.com/kuvaus/LlamaGPTJ-chat/releases). Depending on the
system's security, the pre-compiled program may blocked from running. If that is
the case, you will need to "build" the program in your computer. The instructions
to do this are [here](https://github.com/kuvaus/LlamaGPTJ-chat#download).

### LLM file

The GitHub repoisotry contains a [list of compatible models](https://github.com/kuvaus/LlamaGPTJ-chat#gpt-j-llama-and-mpt-models). 
Download at least one of the models, and make note of where it was saved to
in your computer. 


## Setup

To start, instruct `chattr` to switch the LLamaGPT back-end using `chattr_use()`

```{r}
library(chattr)

chattr_use("llamagpt")
```

If this is the first time you use this interface, confirm that the path of to 
the compiled program, and the model matches to what you have in your machine. 
To check that use `chattr_defaults()`

```{r}
chattr_defaults()
```

If either, or both, paths are incorrect, correct them by updating the `path`,
and `model` arguments in `chattr_defaults()`

```{r}
chattr_defaults(path = "[path to compiled program]", model = "[path to model]")
```

So that you do not need to change those defaults every time you start a new
R session, use `chattr_defaults_save()`. That will create a YAML file in your
working directory. `chattr` will use that file to override the defaults.

```{r, eval = FALSE}
chattr_defaults_save()
```

Use `chattr_test()` to confirm that the `chattr` is able to communicate with 
LLamaGPT-Chat, and that the model it will use with your R session is accessible

```r
chattr_test()
#> ✔ Model started sucessfully
#> ✔ Model session closed sucessfully
```

